experiment 1

### 2021-09-15 experiments/experiment 1/experiment-1.Rmd
WORK IN PROGRESS! Conversion `experiment-1.Rmd` step one

---
title: "experiment 1"
author: "Owen Petchey"
date: "6/25/2021"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

This experiment supercedes all previous ones.
It is a factorial manipulation of diversity of the three groups.
It takes about 50 hours to run while using 12 cores.

@@

microxanox_release <- "0.2"

@@

library(microxanox)
library(tidyverse)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
#options(mc.cores = 8)
eval_dynamics_flag <- FALSE
```

@@

```{r}
default_dynamic_model <- bushplus_dynamic_model
default_event_definition <- event_definition_1
default_event_interval <- 100
default_noise_sigma <- 0
default_minimum_abundances <- rep(1, 3)
names(default_minimum_abundances) <- c("CB", "PB", "SB")
default_sim_duration <- 80000
default_sim_sample_interval <- 100
initial_pars_from <- "bush_ssfig3"
## note that next line (log10a_series is over-ridden with getting stable states)
#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)
```

@@

```{r}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9

## multiplier of SBPB variation
CB_var_multiplier <- 2
SBPB_var_multiplier <- 6

@@

num_div_treatment_levels <- 20
```

@@

```{r}
var_expt <- create_diversity_factorial()
```

@@

```{r}
display_diversity(400)
```

@@

```{r}
var_expt_levels <- var_expt[,1:6]

@@

```{r eval = eval_dynamics_flag}
default_sim_duration <- 80000
```

```{r eval = eval_dynamics_flag}
default_log10a_series <- c(-1, -7, -7)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
sim_res_novar1 <- run_simulation(parameter_values = var_expt$pars[[no_diversity]],
                          initial_state = initial_state)
saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
```

@@

var_expt <- create_diversity_factorial()

display_diversity(4)

>>>>

---
title: "experiment 1"
author: "Owen Petchey"
date: "6/25/2021"
output:
  html_document:
    keep_md: yes
---

This experiment supersedes all previous ones.
It is a factorial manipulation of diversity of the three groups.
It takes about 50 hours to run while using 12 cores.

@@

microxanox_release <- "0.2.3_beta"

@@

library(microxanox)
if (packageVersion("microxanox") < package_version("0.2.3")) {
  stop("microxanox version needs to be at least 0.2.3!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("experiments/r functions/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
#options(mc.cores = 8)
eval_dynamics_flag <- FALSE
```

@@

# default_dynamic_model <- bushplus_dynamic_model
# default_event_definition <- event_definition_1
# default_event_interval <- 100
# default_noise_sigma <- 0
# default_minimum_abundances <- rep(1, 3)
# names(default_minimum_abundances) <- c("CB", "PB", "SB")
# default_sim_duration <- 80000
# default_sim_sample_interval <- 100
# initial_pars_from <- "bush_ssfig3"
## note that next line (log10a_series is over-ridden with getting stable states)
#default_log10a_series <- c(-2, -2, -2, -2, -10, -10, -10, -10, -10)

num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9

sp <- new_strain_parameter(
  n_CB = 9,
  n_PB = 9,
  n_SB = 9,

  values_initial_state = "bush_ssfig3"
)

parameter <- new_runsim_parameter(
  dynamic_model = bushplus_dynamic_model,
  event_definition = event_definition_1,
  event_interval = 100,
  noise_sigma = 0,
  minimum_abundances = rep(0, 3),
  sim_duration = 2000,
  sim_sample_interval = 100,
  strain_parameter = sp,
  log10a_series = c(
    log10(sp$a_O),
    log10(sp$a_O)
  )
)
names(parameter$minimum_abundances) <- c("CB", "PB", "SB")
rm(sp)

@@

```{r}
## multiplier of SBPB variation
CB_var_multiplier <- 2
SBPB_var_multiplier <- 6

@@

num_div_treatment_levels <- 20

@@

```{r}
var_expt <- create_diversity_factorial(
  zero = zero, unity = unity,
  num_div_treatment_levels = num_div_treatment_levels,
  CB_gmax_div = CB_gmax_div, CB_h_div = CB_h_div,
  SB_gmax_div = SB_gmax_div, SB_h_div = SB_h_div,
  PB_gmax_div = PB_gmax_div, PB_h_div = PB_h_div,
  default_9strain = new_strain_parameter(
    n_CB = num_CB_strains,
    n_SB = num_SB_strains,
    n_PB = num_PB_strains,
    values_initial_state =  "bush_ssfig3"
  )
)
```

@@

```{r}
display_diversity(
  400,
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)
```

@@

```{r}
var_expt_levels <- var_expt[, 1:6]

no_diversity <- which(rowSums(abs(var_expt_levels)) == 0)
max_diversty_all <- which(
  max(rowSums(abs(var_expt_levels))) == rowSums(abs(var_expt_levels))
)
max_only_CB_diversity <- which(
  max(rowSums(abs(var_expt_levels[, 1:2]))) == rowSums(abs(var_expt_levels[, 1:2])) &
  rowSums(abs(var_expt_levels[,3:6])) == 0
)
# var_expt_levels[381,]

max_only_SBPB_diversity <- which(
  max(rowSums(abs(var_expt_levels[, 3:6]))) == rowSums(abs(var_expt_levels[, 3:6])) &
  rowSums(abs(var_expt_levels[, 1:2])) == 0
)
#var_expt_levels[20,]

@@

```{r eval = eval_dynamics_flag}
# default_sim_duration <- 80000
parameter$sim_duration <- 80000
```

```{r eval = eval_dynamics_flag}
stop("CHECK PARAMETER VALUES")
# default_log10a_series <- c(-1, -7, -7)
parameter$log10a_series <- c(-1, -7, -7)
parameter$strain_parameter <- var_expt$pars[[no_diversity]]
parameter$strain_parameter$initial_state <- new_initial_state(
  num_CB_strains,
  num_PB_strains,
  num_SB_strains,
  values = "bush_ssfig3"
)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/num_CB_strains
sim_res_novar1 <- run_simulation(parameter)
saveRDS(sim_res_novar1, here("experiments/experiment 1/data/sim_res_novar1.RDS"))
```

@@

var_expt <- create_diversity_factorial(zero = zero, unity = unity, num_div_treatment_levels = num_div_treatment_levels)

display_diversity(
 4,
  var_expt = var_expt,
  num_CB_strains = num_CB_strains,
  num_SB_strains = num_SB_strains,
  num_PB_strains = num_PB_strains
)
